\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-17 doc/USER_MANUAL/manual_SPECFEM3D.tex
added examples for meshfem3D and updated the manual

     \item \texttt{Q}           : 0=no attenuation / standard \texttt{Q} attenuation value

@@

     \item \texttt{domain\_id}        : 1=acoustic / 2=elastic / 3=poroelastic

@@

The file defined in \texttt{INTERFACES\_FILE} contains the settings of the topography grid
and of the interfaces grids. The number
of interfaces, including the topography, needs to be set at the first line. Then, from the bottom
to the top of the model, you need to define the grids with several parameters :
 number of points along $x$ and $y$, minimal $x$ and $y$ coordinates, spacing between points and the file
in which the elevation values are stored. At the end of this file, you simply need to set the
number of spectral elements in the vertical direction for each layer.\\

>>>>

     \item \texttt{Q}           : quality factor

@@

     \item \texttt{domain\_id}        : 1=acoustic / 2=elastic 

@@

The file defined in the \texttt{INTERFACES\_FILE} parameter of \texttt{Mesh\_Par\_File} contains the settings of the topography grid
and of the interfaces grids. The number of interfaces, including the topography, needs to be set at the first line. Then, from the bottom
to the top of the model, you need to define the grids with several parameters : {\texttt{SUPPRESS\_UTM\_PROJECTION}
as described previously, number of points along $x$ and $y$, minimal $x$ and $y$ coordinates, spacing between points and the name of the file 
which contains the elevation values (in $y$.$x$ increasing order).  
At the end of this file, you simply need to set the
number of spectral elements in the vertical direction for each layer. We provide a few models in the {\texttt{examples/}} directory.  \\
